The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-06-04 paper/referee-reply.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Response to the first report on the article draft \emph{The
    Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}} 
\author{Juan N. Garavito-Camargo, Jaime E. Forero-Romero, Mark Disjkstra}
\date{\today}

\begin{document}

\maketitle
We thank the referee for a detailed report. Indeed, the report
motivated us to explore a very important aspect of our results that we
had overlooked.

We made a plot suggested by the referee that showed a clear
dependence of the line morphology with the viewing angle an effect
that we had deemed as negligeable after measuring a proxy statistic for
it (the integrated flux).

@@

The correct interpretation is that, as the referee expected, there is
a strong effect on the morphology.

This completely changed the focus of our paper. We have now completely
rewritten the Results and Discussion section in order to highlight
that result. We have also completeley dropped sections (e.g. the
asymetrical emission part) that obfuscate this main result.

@@

\section{Global Comments}

\subsection{Variation with the viewing angle}

{\bf The problematic of anisotropy is only studied from Sect3.4, the former
sections consider global quantities (spectral shapes, escape
fractions, etc...). This is ok only if there is NO anisotropy induced
by rotation, which is not obvious, a priori. You should make it clear
from the beginning, telling that you will investigate anisotropy at
the end of the paper only, because you checked that lya properties are
isotropic, at least in the range of parameters that you investigated
so far.}

As we mentioned in the introduction to this letter, there is indeed
an anisotropy in the line morphology. The paper was re-structured
accordingly.

However, the properties that we had measured as isotropic (integrated
flux and escape fracrion) remain anisotropic.

@@

{\bf As explained in sect 3.4, rotation kills the spherical symmetry
  of your problem, and the rotation axis defines a preferential
  direction. We could expect some variation of the emerging flux, the
  lyman-alpha escape fraction, and the spectral shape, with viewing
  angle. From Fig8, it seems that the flux is the same in all
  directions for spherical distributions of sources. This important
  result is not enough emphasized.}

We now emphasize in the abstract, section 3.2 and the conclusions the
result on the non-variation of the total flux with viewing angle.

@@

{\bf Do you see any difference in the spectral shape with viewing
  angle? To illustrate this point, it would be interesting to build a
  2D plot as you did on Fig 5, but replace Nb scat in ordinates by the
  viewing angle $\mu$. We could immediatly see if there is an
  evolution of the shape with viewing angle or not. If you find NO
  evolution of the Lya shape with viewing angle, I think that it is an
  interesting counter-intuitive result, that you should advertise
  more.}

As we metioned in the introduction to this reply, we prepared the
suggested plot and found strong variations of the spectral shape with
viewing angle. This result motivated us to re-structure the paper to
emphasize it.

@@

{\bf What about the variation of lya escape fraction with viewing
  angle ? I propose that in the beginning of Sect.3 Results, you first
  emphasize that, maybe counter-intuitively, you did not find any
  variation of the Lya properties with viewing angle, so you will
  present first angle average lya properties, and you will come back
  to the anisotropy problematic only at the end on the paper.}

We do not find any significant dependence of the escape fraction with
the viewing angle. This is shown in Figure \ref{escape_fraction} of this
document. We do not show this plot in the paper and only mention the
result at the beginning of Section 3.5.

\begin{figure}
\includegraphics[scale=0.5]{escapefractionvstheta.png}
\caption{Escape Fraction as a function of $\mu$
\label{escape_fraction}}
\end{figure}

@@

\subsection*{Fig.1}

{\bf I guess that the spectra presented in Fig1 are integrated over all directions, right ? You should describe explicitly how you build them. You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.}

Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency

\begin{itemize}
\item Description about how we build Fig.1 (Done)
\item Fig 1. remove x notation (Done)
\end{itemize}

### 2014-06-04 paper/ms.tex
minor updates

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f5.pdf}
\end{center}
\caption{Integrated flux distribution as a function of the
  viewing angle as parameterized by $\mu$. Continous (dashed)
  correspond to central (homogeneous) source distribution.
  The models correspond to an optical depth of $\tau_{\rm
    H}=10^5$ and rotational velocities of $100$\kms, $200$\kms and
  $300$\kms. The distributions are flat, meaning that the integrated
  flux for all viewing angles is the same.
\label{fig:muhisto}}
\end{figure}

@@

This is a remarkable result. In spite of that the rotation axis
defines preferential direction, the integrated flux is the same for
all viewing angles and all the possible models in our spherical
distributions.

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f5.pdf}
\end{center}
\caption{Integrated flux distribution as a function of the
  viewing angle as parameterized by $\mu$. Continous (dashed)
  correspond to central (homogeneous) source distribution.
  The models correspond to an optical depth of $\tau_{\rm
    H}=10^5$ and rotational velocities of $100$\kms, $200$\kms and
  $300$\kms. The distributions are flat in the range of models probed
  in this paper, meaning that the integrated flux for all viewing angles is the same.
\label{fig:muhisto}} 
\end{figure}

@@

This is a remarkable result. In spite of that the rotation axis
defines preferential direction, the integrated flux is the same for
all viewing angles, at least for the range of parameters explored in
this paper.
